---
title: "Aggie treeline field experiment data"
output: 
  github_document:
  html_preview: True
  
---

```{r setup, include=FALSE, echo=FALSE}
library(targets)
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE
                      )
```

## sample summary

<details>
  <summary>click to open</summary>

Soils were collected around trees on treelines in the western brooks range Alaska varying in soil moisture. Three sites were chosen: Tussock tundra (Mesic), Wet Sedge (Hydric), and Dryas-lichen tundra (Xeric). 8 similar trees were chosen per treatment based on their DBH and proximity to the treeline. Snow fences were constructed as a treatment to build larger snow packs around the given trees in winter and compared against a control group where nothing was done besides sampling. In order to reduce impact on these tree-plots 8 Ancillary trees were also chosen based on the same DBH, proximity to treeline parameters and used for seasonal sampling.   
  A previous project conducted at these sites fertilized soils around similar trees. These soils were also sampled to identify long term effects of fertilization. 
  Soils were collected from control and snowfence trees in march and late may/early June (Just after thaw) along with resin strips (Except in 2020). Soil pore water was taken regularly during the growing season (2017-2019). During 2019 collection frequencies reduced due to staffing and were disrupted due to COVID in 2020 with an inability to visit the field sites. 

```{r setup, include=FALSE, echo=FALSE}
```

</details>

---

##   Snowfence Vs. Control

<details>
  <summary>click to open</summary>
  
 #### Extracts:
  
  K2SO4 
  
  <details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_Extract_Snowfence_Control)
```
<details>
  <summary>click to open ANOVA results</summary>
  
```{r , fig.height=6, fig.width=6}
tar_read(gg_aggie_Extract_Snowfence_Control)$Extract_Snowfence_aov2
tar_read(gg_aggie_Extract_Snowfence_Control)$Extract_Snowfence_aov3
```
  
</details>
</details>

#### H2O: 

  <details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_Extract_Snowfence_Control_H2O)
```
 <details>
  <summary>click to open ANOVA results</summary>
  
```{r , fig.height=6, fig.width=6}
tar_read(gg_aggie_Extract_Snowfence_Control_H2O)$Extract_Snowfence_aov2_H2O
tar_read(gg_aggie_Extract_Snowfence_Control_H2O)$Extract_Snowfence_aov3_H2O
```

</details>
</details>



#### Pore water:
 
  <details>
  <summary>click to open</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_PoreWater_Snowfence_Control)
```
<details>
  <summary>click to open</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_PoreWater_Snowfence_Control)
```
<details>
  <summary>click to open LME results</summary>
  
 

```{r , fig.height=6, fig.width=6}
tar_read(gg_aggie_PoreWater_Snowfence_Control)$Porewater_Snowfence_LME2
tar_read(gg_aggie_PoreWater_Snowfence_Control)$Porewater_Snowfence_LME
```

</details>
</details>
</details>

#### Resin strip:
 
  <details>
  <summary>click to open</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_resin_Snowfence)
```


<details>
  <summary>click to open ANOVA results</summary>
  
 Differences between sites.

```{r , fig.height=6, fig.width=6}
tar_read(gg_resin_Snowfence)$Extract_resin_aov3
tar_read(gg_resin_Snowfence)$Extract_resin_aov2
```

</details>
</details>


</details>


---

## Seasonal Extracts and pore water (Ancillary plots)
<details>
  <summary>click to open</summary>
  
 #### Extracts:
 Due to soil plot concerns only ancillary plots were harvested multiple times per year.
  K2SO4:
  
  <details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Extract_Seasonal)
```

</details>

#### H2O:

<details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Extract_Seasonal_H2O)
```

</details>



#### Pore water:
 
  <details>
  <summary>click to open</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_PoreWater_Seasonal)
```
<details>
  <summary>click to open LME results</summary>
  
 

```{r , fig.height=6, fig.width=6}
tar_read(gg_aggie_PoreWater_Seasonal)$Porewater_Seasonal_LME
tar_read(gg_aggie_PoreWater_Seasonal)$Porewater_Seasonal_LME2
```

</details>
</details>

#### Resin strip:
 
  <details>
  <summary>click to open</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_resin_Ancillary)
```
</details>

</details>

---


## Treeline project Extracts and pore water (Ancillary, Control, Snowfence plots)

<details>
  <summary>click to open</summary>
  
#### Extracts:
 Due to soil plot concerns only ancillary plots were harvested multiple times per year.
  K2SO4:
  
  <details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Extract_all)
```

</details>

#### H2O:

<details>

  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Extract_all_H2O)
```

</details>



#### Pore water:
 
  <details>
  
  <summary>click to open</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_PoreWater_all)
```
<details>
  
  <summary>click to open LME results</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_PoreWater_all)$Porewater_all_LME
tar_read(gg_aggie_PoreWater_all)$Porewater_all_LME2
```

</details>
</details>

#### Resin strip:

<details>
  <summary>click to open</summary>
  
  Resin strips were extracted in 2M KCl
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_resin)
```


</details>


</details>

---

## All Extracts and pore water (Ancillary, Control, Snowfence, and fertilized plots)

<details>
  <summary>click to open</summary>
  
#### Extracts:
 Due to soil plot concerns only ancillary plots were harvested multiple times per year.
  K2SO4:
  
  <details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Extract_Fert)
```

</details>

#### H2O:

<details>

  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Extract_H2O_Fert)
```

</details>



#### Pore water:
 
  <details>
  
  <summary>click to open</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Porewater_Fert)
```
<details>
  
  <summary>click to open LME results</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Porewater_Fert)$Porewater_LME
tar_read(gg_Porewater_Fert)$Porewater_LME2
```

</details>
</details>

#### Resin strip:

<details>
  <summary>click to open</summary>
  
  Resin strips were extracted in 2M KCl
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Resin_Fert)
```


</details>


</details>

---

## Destructive lysimeter test

<details>
  <summary>click to open</summary>

#### Pore water:

<details>
  <summary>click to open</summary>


```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_aggie_PoreWater_Lysim)
```

</details>

#### Extractions

<details>
  <summary>click to open</summary>


```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_Extract_lysim)
```

</details>

</details>

---

## FTICR analysis

<details>
  <summary>click to open</summary>

Homogenized soil samples collected in the field in early(end of may begining of June) and late spring (Late June or early July) from 2017, 2018 and 2019 were sent to EMSL for FTICR analysis. 

#### 1. FTICR domains 

<details>
  <summary>click to open</summary>



```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_fticr_Domains)
```





</details>

#### 2. Comparing polar vs. non-polar extracts

<details>
  <summary>click to open</summary>


```{r, fig.height=6, fig.width=6}
tar_load(gg_polarVnonpolar_vk) 
ggExtra::ggMarginal(gg_polarVnonpolar_vk, groupColour = TRUE, groupFill = TRUE, alpha = 0.1)

```

```{r, fig.height=6, fig.width=6}
tar_read(gg_polarVnonpolar_pca) 
```

Non-polar extracts were strongly dominated by low-O aliphatic molecules and skewed the overall trends when we combined results from polar and non-polar extracts. 
We therefore analyze the two extract types separately, and focus primarily on the polar (water) extracts.


</details>


#### 3. Polar extracts

<details>
  <summary>click to open</summary>
  

###### 3.1. PERMANOVA

<details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6}
tar_read(Permanova_table_polar)
```

Site, Site:Year were significant (p < 0.05)

Site accounted for 71 % of total variation among samples (R2= 0.71)

</details>




###### 3.2. PCA

<details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_pca_by_site)
```


There was a strong separation among the three Site/soil types. Hydric and Xeric soils were strongly dominated by aliphatic (simple) molecules, whereas Mesic soils were dominated by lignin-like, aromatic, and condensed aromatic (complex) molecules.


```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_pca_polar)
```


Hydric Only

```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_pca_hydric)
```

</details>

###### 3.3. Van Krevelen 

<details>
  <summary>click to open</summary>



3.3.1. All treatments
<details>
  <summary>click to open</summary>

```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_vk_polar)
```

</details>



3.3.2. Unique peaks by site
<details>
  <summary>click to open</summary>

```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_unique)
```

```{r , fig.height=6, fig.width=6}
tar_read(gg_unique2)
```

</details>



3.3.3. Seasonality Mesic and Hydric
<details>
  <summary>click to open</summary>

```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_seasonal)
```

</details>

</details>

</details>

  
</details>

---

## Session Info 

<details>
  <summary> Session Info </summary>

Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>