---
title: "Antecedent temperature experiment"
output: 
  github_document:
  html_preview: True
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE
                      )
```

## sample summary

<details>
  <summary>click to open</summary>

```{r analyte-completion, eval= TRUE}
```

</details>

---

##   Snowfence Vs. Control

<details>
  <summary>click to open</summary>
  
 #### Extracts:
  
  K2SO4 
  
  <details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_Extract_Snowfence_Control)
```

</details>

H2O: 

  <details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_Extract_Snowfence_Control_H2O)
```

</details>



 #### Pore water:
 
  <details>
  <summary>click to open</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_PoreWater_Snowfence_Control)
```

</details>

</details>


---

## Seasonal Extracts and pore water
<details>
  <summary>click to open</summary>
  
 #### Extracts:
 Due to soil plot concerns only ancillary plots were harvested multiple times per year.
  K2SO4:
  
  <details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Extract_Seasonal)
```

</details>

H2O:

<details>
  <summary>click to open</summary>
  
```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_Extract_Seasonal_H2O)
```

</details>



 #### Pore water:
 
  <details>
  <summary>click to open</summary>
  
 

```{r , fig.height=6, fig.width=6, results='hide', out.width="100%"}
tar_read(gg_aggie_PoreWater_Seasonal)
```

</details>

</details>

---

## Destructive lysimeter test
<details>
  <summary>click to open</summary>


```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_aggie_PoreWater_Lysim)
```

</details>

---

## Session Info 

<details>
  <summary> Session Info </summary>

Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>