---
title: "FTICR-MS report"
output: 
  github_document:
    html_preview: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      error = FALSE,
                      warning = FALSE)
```


## Research questions/hypotheses:



---

```{r setup_script}

source("code/0-packages.R")
source("code/fticrrr/b-functions_analysis.R")

# 1. load files -----------------------------------------------------------

fticr_meta  = read.csv("data/processed/fticr_meta_combined.csv")
fticr_data_longform = read.csv("data/processed/fticr_data_longform_combined.csv")
fticr_data_trt = read.csv("data/processed/fticr_data_trt_combined.csv")

## SET the treatment variables
## this will work with multiple variables too. just add all the variable names in the parentheses.
TREATMENTS = dplyr::quos(Site, Year, Season, Polar)

options(ggplot2.discrete.color = PNWColors::pnw_palette("Bay", 3))
```

```{r}
reorder_seasons = function(dat){
  dat %>% mutate(Season = factor(Season, levels = c("Spring", "LateSpring", "Fall")))
}

reorder_sites = function(dat){
  dat %>% mutate(Site = factor(Site, levels = c("Xeric", "Mesic", "Hydric")))
  
}

```


----

## 1. FTICR domains 

```{r, domains, fig.height=5, fig.width=5}
#gg_vk_domains = 
  gg_vankrev(fticr_meta, aes(x = OC, y = HC, color = Class))+
  scale_color_manual(values = PNWColors::pnw_palette("Sunset2"))+
  theme_kp()

#gg_vk_domains_nosc = 
  gg_vankrev(fticr_meta, aes(x = OC, y = HC, color = as.numeric(NOSC)))+
  scale_color_gradientn(colors = PNWColors::pnw_palette("Bay"))+
  theme_kp()
```


```{r}
fticr_hcoc = 
  fticr_data_trt %>% 
  reorder_seasons() %>% reorder_sites() %>% 
  left_join(dplyr::select(fticr_meta, formula, HC, OC), by = "formula")
```

```{r}
relabund_cores = 
  fticr_data_longform %>% 
  compute_relabund_cores(fticr_meta, TREATMENTS) %>% 
  reorder_seasons() %>% reorder_sites()
```

## 2. Comparing polar vs. non-polar extracts

```{r vk_polar_nonpolar, fig.height=5, fig.width=5}
#gg_vk_polar_nonpolar = 
  (fticr_hcoc %>%
  distinct(formula, HC, OC, Polar) %>% 
  gg_vankrev(aes(x = OC, y = HC, color = Polar))+
  stat_ellipse(level = 0.90, show.legend = FALSE)+
  theme(legend.position = c(0.8, 0.8)) +
  NULL) %>% 
  # include marginal density plots
  ggExtra::ggMarginal(groupColour = TRUE, groupFill = TRUE, alpha = 0.1)
```

```{r pca_polar_nonpolar}
pca_all = fit_pca_function(relabund_cores)

(gg_pca_polar_nonpolar = 
    ggbiplot(pca_all$pca_int, obs.scale = 1, var.scale = 1,
             groups = as.character(pca_all$grp$Polar), 
             ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
    geom_point(size=3,stroke=1, alpha = 0.5,
               aes(#shape = groups,
                 color = groups))+
    #scale_shape_manual(values = c(21, 22, 19), name = "", guide = "none")+
    xlim(-4,4)+
    ylim(-3.5,3.5)+
    labs(shape="",
         title = "all samples",
         subtitle = "polar vs. nonpolar")+
    theme_kp()+
    NULL
)
```

Non-polar extracts were strongly dominated by low-O aliphatic molecules and skewed the overall trends when we combined results from polar and non-polar extracts. 
We therefore analyze the two extract types separately, and focus primarily on the polar (water) extracts.


---

## 3. Polar extracts

```{r}
fticr_hcoc_polar = fticr_hcoc %>% filter(Polar == "polar") 
relabund_cores_polar = relabund_cores %>% filter(Polar == "polar") 
```

### 3.1. PERMANOVA

```{r PERMANOVA_polar}

# you need to convert the rel-abundance file into wide form

relabund_wide = 
  relabund_cores_polar %>% 
  ungroup() %>% 
  mutate(Class = factor(Class, 
                        levels = c("aliphatic", "unsaturated/lignin", 
                                   "aromatic", "condensed aromatic"))) %>% 
  dplyr::select(-c(abund, total)) %>% 
  spread(Class, relabund) %>% 
  replace(is.na(.), 0)

# adonis function for PERMANOVA
permanova_fticr_all = 
  adonis(relabund_wide %>% dplyr::select(aliphatic:`condensed aromatic`) ~ (Site + Year + Season)^2, 
         data = relabund_wide) 

knitr::kable(permanova_fticr_all$aov.tab)

```

Site, Site:Year were significant (p < 0.05)

Site accounted for 71 % of total variation among samples (R2= 0.71)


### 3.2. PCA

```{r}

pca_polar = fit_pca_function(relabund_cores %>% filter(Polar == "polar"))

```


```{r gg_pca_site}

(gg_pca_by_site = 
  ggbiplot(pca_polar$pca_int, obs.scale = 1, var.scale = 1,
           groups = as.character(pca_polar$grp$Site), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=3,stroke=1, alpha = 1,
             aes(#shape = groups,
                 color = groups))+
  #scale_shape_manual(values = c(21, 22, 19), name = "", guide = "none")+
  xlim(-4,4)+
  ylim(-3.5,3.5)+
  labs(shape="",
       title = "all samples",
       subtitle = "separation by Site")+
  theme_kp()+
  NULL
)

```

There was a strong separation among the three Site/soil types. Hydric and Xeric soils were strongly dominated by aliphatic (simple) molecules, whereas Mesic soils were dominated by lignin-like, aromatic, and condensed aromatic (complex) molecules.


```{r gg_pca_polar}
(gg_pca_by_year = 
    ggbiplot(pca_polar$pca_int, obs.scale = 1, var.scale = 1,
             groups = as.character(pca_polar$grp$Year), 
             ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
    geom_point(size=3,stroke=1, alpha = 1,
               aes(
                 #shape = as.character(pca_polar$grp$Site),
                 color = groups))+
    #scale_shape_manual(values = c(21, 22, 19), name = "", guide = "none")+
    xlim(-4,4)+
    ylim(-3.5,3.5)+
    labs(shape="",
         title = "all samples",
         subtitle = "separation by Site")+
    theme_kp()+
    NULL
)


(gg_pca_by_season = 
    ggbiplot(pca_polar$pca_int, obs.scale = 1, var.scale = 1,
             groups = as.character(pca_polar$grp$Season), 
             ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
    geom_point(size=3,stroke=1, alpha = 1,
               aes(#shape = groups,
                 color = groups))+
    #scale_shape_manual(values = c(21, 22, 19), name = "", guide = "none")+
    xlim(-4,4)+
    ylim(-3.5,3.5)+
    labs(shape="",
         title = "all samples",
         subtitle = "separation by Site")+
    theme_kp()+
    NULL
)

```


Hydric Only

```{r gg_pca_hydric}

# Hydric only
pca_hydric = fit_pca_function(relabund_cores %>% filter(Polar == "nonpolar" & Site == "Hydric"))

(gg_pca_hydric = 
    ggbiplot(pca_hydric$pca_int, obs.scale = 1, var.scale = 1,
             groups = as.character(pca_hydric$grp$Season), 
             ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
    geom_point(size=3,stroke=1, alpha = 1,
               aes(shape = as.character(pca_hydric$grp$Year),
                 color = groups))+
    #scale_shape_manual(values = c(21, 22, 19), name = "", guide = "none")+
    xlim(-4,4)+
    ylim(-3.5,3.5)+
    labs(shape="",
         title = "Hydric samples",
         subtitle = "separation by Season")+
    theme_kp()+
    NULL
)

```


### 3.3. Van Krevelen 

#### 3.3.1. All treatments

```{r vk_all, fig.height=7, fig.width=7}

#gg_vk_all = 
  gg_vankrev(fticr_hcoc_polar, aes(x = OC, y = HC, color = Site))+
  stat_ellipse(level = 0.90, show.legend = FALSE)+
  facet_grid(Season ~ Polar + Year)+
  NULL

```

```{r vk_site, fig.height=5, fig.width=12}

#gg_vk_all_site = 
  gg_vankrev(fticr_hcoc_polar, aes(x = OC, y = HC, color = as.character(Year)))+
  stat_ellipse(level = 0.90, show.legend = FALSE)+
  facet_grid(. ~ Site)+
  NULL

```


#### 3.3.2. Unique peaks by site

```{r vk_unique_site, fig.height=5, fig.width=12}

fticr_unique_site = 
  fticr_hcoc %>% 
  distinct(formula, Site, HC, OC) %>% 
  group_by(formula) %>% 
  dplyr::mutate(n = n())

# overlay unique peaks onto common peaks
#gg_site_common_unique = 
    fticr_unique_site %>% filter(n == 3) %>% 
    gg_vankrev(aes(x = OC, y = HC))+
    geom_point(data = fticr_unique_site %>% filter(n == 1),
               aes(color = Site), alpha = 0.7)+
    facet_wrap(~Site)+
    labs(title = "Unique peaks at each Site",
         subtitle = "black/grey = peaks common to all")+
    NULL

```

Summary of unique peaks
```{r}

## summarize unique peaks
#fticr_unique_site_summary = 
  fticr_unique_site %>% 
  filter(n == 1) %>% 
  left_join(fticr_meta %>% dplyr::select(formula, Class)) %>% 
  group_by(Site, Class) %>% 
  dplyr::summarise(counts = n()) %>% 
  pivot_wider(names_from = "Site", values_from = "counts") %>% 
  knitr::kable()

```


---

#### 3.3.3. Seasonality

```{r}
fticr_hcoc_polar_mesic_hydric = 
  fticr_hcoc_polar %>% 
  filter(Site %in% c("Mesic", "Hydric"))
```

```{r vk_season, fig.width=8, fig.height=6}

fticr_hcoc_polar_mesic_hydric %>% 
  gg_vankrev(aes(x = OC, y = HC, color = Season))+
  facet_grid(Site ~ Year)
```



---

<details>
  <summary>Session Info</summary>
  
  
  Date run: `r Sys.Date()`
```{r}
sessionInfo()
```
  
  </details>