---
title: "FTICR_FIELD_TREELINE_NONPOLAR_CKM"
output: pdf_document
---

## Read in Libraries and set working directory
```{r, echo=FALSE }
library(ftmsRanalysis)
library(dplyr)
library(tidyr)
library(purrr)
library(rbokeh)
library(ggplot2)
library(devtools)
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

```

## e_data (Expression Data)
```{r}
dat_edata <- read.csv(file="Field_NonPolar_Edata.csv", header=TRUE, sep=",")
```

## f_data (Sample Data)
```{r}
dat_fdata <- read.csv(file="Field_NonPolar_Fdata.csv", header=TRUE, sep=",")
dat_fdata$ID <- gsub("-",".",dat_fdata$ID)

```

## e_meta (Molecular Identification Data)
```{r }
dat_emeta <- read.csv(file="Field_NonPolar_Emeta.csv", header=TRUE, sep=",")

```

## Constructing a peakData object
```{r}
peakObj <- as.peakData(dat_edata, dat_fdata, dat_emeta,edata_cname="Mass", fdata_cname="ID", mass_cname="Mass", c_cname="C", h_cname="H", o_cname="O", n_cname="N", s_cname="S", p_cname="P", isotopic_cname = "C13", isotopic_notation = "1")
peakObjA<-peakObj

```

# Preprocessing

## Transforming abundance values
```{r}
peakObj <- edata_transform(peakObj, data_scale="log2")

plot(peakObj)
```

## Calculating meta-data
```{r}
peakObj <- compound_calcs(peakObj)
```
## Elemental Composition Breakdown
```{r}
peakObj <- assign_elemental_composition(peakObj)

table(peakObj$e_meta[,getElCompColName(peakObj)])
```
## Compound Class Breakdown using Boundary Set 2 (Bailey 2017)
```{r}
peakObj <- assign_class(peakObj, boundary_set = "bs2")
table(peakObj$e_meta[, getBS2ColName(peakObj)])
```

There are three sets of class boundary definitions that may be used (for the `boundary_set` parameter) corresponding to the following publications:

* `bs1` - [Kim, S., et al (2003). Analytical Chemistry.](https://dx.doi.org/10.1021/ac034415p){target="_blank"}
* `bs2` - [Bailey, V. et al (2017). Soil Biology and Biochemistry.](https://dx.doi.org/10.1016/j.soilbio.2016.11.025){target="_blank"}
* `bs3` - [Rivas-Ubach, A., et al (2018). Analytical chemistry.](https://dx.doi.org/10.1021/acs.analchem.8b00529){target="_blank"}

## Filtering

## Filter data without formula
```{r}
peakObj <- applyFilt(formula_filter(peakObj), peakObj)
summary(peakObj)
```

## Combinung emeta, fdata, and edata to calculate the sample means
```{r}
# combine
alldata <- tidyr::gather(peakObj$e_data, key="ID", value="Intensity", -Mass) %>%
  dplyr::full_join(peakObj$e_meta, by="Mass") %>%
  dplyr::full_join(peakObj$f_data, by="ID") %>%
  dplyr::filter(Intensity > 0 & !is.na(Intensity))

Sample.KeyValues <- alldata %>%
  dplyr::group_by(ID, Site) %>%
  dplyr::summarise(MeanNOSC = mean(NOSC),
                   MeanDBE = mean(DBE),
                   MeanDBE_O = mean(DBE_O), 
                   MeanAI = mean(AI),
                   MeanHtoC = mean(HtoC_ratio), 
                   MeanOtoC = mean(OtoC_ratio), 
                   MeanNtoC = mean(NtoC_ratio),
                   MeanNtoP = mean(NtoP_ratio),
                   MeanNtoP = mean(NtoP_ratio, na.rm=TRUE),
                   MeanPtoC = mean(PtoC_ratio),
                   MeanGFE = mean(GFE))

View(Sample.KeyValues)

Sample.KeyValues2 <- alldata %>%
  dplyr::group_by(ID, Site, Class, Year) %>%
  dplyr::summarise(MeanNOSC = mean(NOSC),
                   MeanDBE = mean(DBE),
                   MeanDBE_O = mean(DBE_O), 
                   MeanAI = mean(AI),
                   MeanHtoC = mean(HtoC_ratio), 
                   MeanOtoC = mean(OtoC_ratio), 
                   MeanNtoC = mean(NtoC_ratio),
                   MeanNtoP = mean(NtoP_ratio),
                   MeanNtoP = mean(NtoP_ratio, na.rm=TRUE),
                   MeanPtoC = mean(PtoC_ratio),
                   MeanGFE = mean(GFE))


Sample.KeyValuesT <- alldata %>%
  dplyr::group_by(ID, Season) %>%
  dplyr::summarise(MeanNOSC = mean(NOSC),
                   MeanDBE = mean(DBE),
                   MeanDBE_O = mean(DBE_O), 
                   MeanAI = mean(AI),
                   MeanHtoC = mean(HtoC_ratio), 
                   MeanOtoC = mean(OtoC_ratio), 
                   MeanNtoC = mean(NtoC_ratio),
                   MeanNtoP = mean(NtoP_ratio),
                   MeanNtoP = mean(NtoP_ratio, na.rm=TRUE),
                   MeanPtoC = mean(PtoC_ratio),
                   MeanGFE = mean(GFE))


Sample.KeyValuesA <- alldata %>%
  dplyr::group_by(ID, Season, Site) %>%
  dplyr::summarise(MeanNOSC = mean(NOSC),
                   MeanDBE = mean(DBE),
                   MeanDBE_O = mean(DBE_O), 
                   MeanAI = mean(AI),
                   MeanHtoC = mean(HtoC_ratio), 
                   MeanOtoC = mean(OtoC_ratio), 
                   MeanNtoC = mean(NtoC_ratio),
                   MeanNtoP = mean(NtoP_ratio),
                   MeanNtoP = mean(NtoP_ratio, na.rm=TRUE),
                   MeanPtoC = mean(PtoC_ratio),
                   MeanGFE = mean(GFE))
```
## Data Exploration
```{r}
 NtoC <-ggplot(data=Sample.KeyValues, aes(x=Site, y=MeanNtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
NtoC
 NOSC <-ggplot(data=Sample.KeyValues, aes(x=Site, y=MeanNOSC, fill=Site))+
  geom_boxplot()+
  theme_bw()
NOSC
DBE <-ggplot(data=Sample.KeyValues, aes(x=Site, y=MeanDBE, fill=Site))+
  geom_boxplot()+
  theme_bw()
DBE
DBE_O <-ggplot(data=Sample.KeyValues, aes(x=Site, y=MeanDBE_O, fill=Site))+
  geom_boxplot()+
  theme_bw()
DBE_O
AI <-ggplot(data=Sample.KeyValues, aes(x=Site, y=MeanAI, fill=Site))+
  geom_boxplot()+
  theme_bw()
AI
HtoC <-ggplot(data=Sample.KeyValues, aes(x=Site, y=MeanHtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
HtoC
OtoC <-ggplot(data=Sample.KeyValues, aes(x=Site, y=MeanOtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
OtoC
NtoP <-ggplot(data=Sample.KeyValues, aes(x=Site, y=MeanNtoP, fill=Site))+
  geom_boxplot()+
  theme_bw()
NtoP
PtoC <-ggplot(data=Sample.KeyValues, aes(x=Site, y=MeanPtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
PtoC
GFE <-ggplot(data=Sample.KeyValues, aes(x=Site, y=MeanGFE, fill=Site))+
  geom_boxplot()+
  theme_bw()
GFE






```
## Data Exploration2
```{r}
Sample.KeyValues2$Site<-as.factor(Sample.KeyValues2$Site)
Sample.KeyValues2$Year<-as.factor(Sample.KeyValues2$Year)
 NtoC <-ggplot(data=Sample.KeyValues2, aes(x=Year, y=MeanNtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
NtoC
 NOSC <-ggplot(data=Sample.KeyValues2, aes(x=Year, y=MeanNOSC, fill=Site))+
  geom_boxplot()+
  theme_bw()
NOSC
DBE <-ggplot(data=Sample.KeyValues2, aes(x=Year, y=MeanDBE, fill=Site))+
  geom_boxplot()+
  theme_bw()
DBE
DBE_O <-ggplot(data=Sample.KeyValues2, aes(x=Year, y=MeanDBE_O, fill=Site))+
  geom_boxplot()+
  theme_bw()
DBE_O
AI <-ggplot(data=Sample.KeyValues2, aes(x=Year, y=MeanAI, fill=Site))+
  geom_boxplot()+
  theme_bw()
AI
HtoC <-ggplot(data=Sample.KeyValues2, aes(x=Year, y=MeanHtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
HtoC
OtoC <-ggplot(data=Sample.KeyValues2, aes(x=Year, y=MeanOtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
OtoC
NtoP <-ggplot(data=Sample.KeyValues2, aes(x=Year, y=MeanNtoP, fill=Site))+
  geom_boxplot()+
  theme_bw()
NtoP
PtoC <-ggplot(data=Sample.KeyValues2, aes(x=Year, y=MeanPtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
PtoC
GFE <-ggplot(data=Sample.KeyValues2, aes(x=Year, y=MeanGFE, fill=Site))+
  geom_boxplot()+
  theme_bw()
GFE






```
## Data Exploration3
```{r}

 NtoC <-ggplot(data=Sample.KeyValuesT, aes(x=Site, y=MeanNtoC, fill=Class))+
  geom_boxplot()+
  theme_bw()
NtoC
 NOSC <-ggplot(data=Sample.KeyValuesT, aes(x=Site, y=MeanNOSC, fill=Site))+
  geom_boxplot()+
  theme_bw()
NOSC
DBE <-ggplot(data=Sample.KeyValuesT, aes(x=Site, y=MeanDBE, fill=Site))+
  geom_boxplot()+
  theme_bw()
DBE
DBE_O <-ggplot(data=Sample.KeyValuesT, aes(x=Site, y=MeanDBE_O, fill=Site))+
  geom_boxplot()+
  theme_bw()
DBE_O
AI <-ggplot(data=Sample.KeyValuesT, aes(x=Site, y=MeanAI, fill=Site))+
  geom_boxplot()+
  theme_bw()
AI
HtoC <-ggplot(data=Sample.KeyValuesT, aes(x=Site, y=MeanHtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
HtoC
OtoC <-ggplot(data=Sample.KeyValuesT, aes(x=Site, y=MeanOtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
OtoC
NtoP <-ggplot(data=Sample.KeyValuesT, aes(x=Site, y=MeanNtoP, fill=Site))+
  geom_boxplot()+
  theme_bw()
NtoP
PtoC <-ggplot(data=Sample.KeyValuesT, aes(x=Site, y=MeanPtoC, fill=Site))+
  geom_boxplot()+
  theme_bw()
PtoC
GFE <-ggplot(data=Sample.KeyValuesT, aes(x=Site, y=MeanGFE, fill=Site))+
  geom_boxplot()+
  theme_bw()
GFE






```
## Data Exploration4
```{r}

 NtoC <-ggplot(data=Sample.KeyValuesA, aes(x=Season, y=MeanNtoC, fill=Site))+
   scale_fill_manual(values=cbPalette)+
  geom_boxplot()+
  theme_bw()
NtoC
 NOSC <-ggplot(data=Sample.KeyValuesA, aes(x=Season, y=MeanNOSC, fill=Site))+
  geom_boxplot()+
   scale_fill_manual(values=cbPalette)+
  theme_bw()+
   theme(legend.direction = 'vertical', 
        legend.key = element_rect(size=2),
        legend.key.size = unit(3, 'lines'),
        panel.grid.major = element_blank(), 
        legend.title=element_text(size=40,colour='black'),
        panel.grid.minor = element_blank(),
        legend.text=element_text(size=35),
        axis.title.y= element_text(size=40, colour='black'),
        axis.text.y = element_text(size=40, colour='black'),
        axis.ticks = element_line(colour = "black", size=2),
        axis.ticks.length = unit(0.3, "cm"),
        axis.title.x=element_text(size=40, colour='black'),
        axis.text.x = element_text(size=40, colour='black'),
        panel.border = element_rect(colour = "black", fill=NA, size=2),
        plot.title = element_text( size=40, face="bold.italic"),
        plot.margin=unit(c(1,1,1,1), "cm"))
NOSC
DBE <-ggplot(data=Sample.KeyValuesA, aes(x=Season, y=MeanDBE, fill=Site))+
  geom_boxplot()+
  scale_fill_manual(values=cbPalette)+
  theme_bw()
DBE
DBE_O <-ggplot(data=Sample.KeyValuesA, aes(x=Season, y=MeanDBE_O, fill=Site))+
  geom_boxplot()+
  scale_fill_manual(values=cbPalette)+
  theme_bw()
DBE_O
AI <-ggplot(data=Sample.KeyValuesA, aes(x=Season, y=MeanAI, fill=Site))+
  geom_boxplot()+
  scale_fill_manual(values=cbPalette)+
  theme_bw()
AI
HtoC <-ggplot(data=Sample.KeyValuesA, aes(x=Season, y=MeanHtoC, fill=Site))+
  geom_boxplot()+
  scale_fill_manual(values=cbPalette)+
  theme_bw()
HtoC
OtoC <-ggplot(data=Sample.KeyValuesA, aes(x=Season, y=MeanOtoC, fill=Site))+
  geom_boxplot()+
  scale_fill_manual(values=cbPalette)+
  theme_bw()
OtoC
NtoP <-ggplot(data=Sample.KeyValuesA, aes(x=Season, y=MeanNtoP, fill=Site))+
  geom_boxplot()+
  scale_fill_manual(values=cbPalette)+
  theme_bw()
NtoP
PtoC <-ggplot(data=Sample.KeyValuesA, aes(x=Season, y=MeanPtoC, fill=Site))+
  geom_boxplot()+
  scale_fill_manual(values=cbPalette)+
  theme_bw()
PtoC
GFE <-ggplot(data=Sample.KeyValuesA, aes(x=Season, y=MeanGFE, fill=Site))+
  geom_boxplot()+
  scale_fill_manual(values=cbPalette)+
  theme_bw()+
  theme(legend.direction = 'vertical', 
        legend.key = element_rect(size=2),
        legend.key.size = unit(3, 'lines'),
        panel.grid.major = element_blank(), 
        legend.title=element_text(size=40,colour='black'),
        panel.grid.minor = element_blank(),
        legend.text=element_text(size=35),
        axis.title.y= element_text(size=40, colour='black'),
        axis.text.y = element_text(size=40, colour='black'),
        axis.ticks = element_line(colour = "black", size=2),
        axis.ticks.length = unit(0.3, "cm"),
        axis.title.x=element_text(size=40, colour='black'),
        axis.text.x = element_text(size=40, colour='black'),
        panel.border = element_rect(colour = "black", fill=NA, size=2),
        plot.title = element_text( size=40, face="bold.italic"),
        plot.margin=unit(c(1,1,1,1), "cm"))
GFE


ggsave('GFE.png', plot=GFE, width= 20, height= 12)
ggsave('NOSC.png', plot=NOSC, width= 20, height= 12)



```
## Calculating PCA values from peak data and getting the data back into a numeric form. Combining data with sample means calculated in KeyValues.
```{r}
pca<-getPrincipalCoordinates(peakObjA)
attr(pca,"R^2")

d <- pca
ID <- rownames(d)
rownames(d) <- NULL
data <- cbind(ID,d)
data<- as.data.frame(data)

PCA2<- merge(Sample.KeyValuesA, data,by.x="ID", by.y="ID", sort = TRUE)

PCA2[, c(4:17)] <- sapply(PCA2[, c(4:17)], as.numeric)

```

##Plotting Stat Ellipises on PCA plot
```{r}
PCA2$Site<-as.factor(PCA2$Site)
PCA2$Season<-as.factor(PCA2$Season)
PCA1<-ggplot(PCA2, aes(x=Axis.1, y=Axis.2, color=Site))+
  geom_point(lwd=4)+
  stat_ellipse(aes(x=Axis.1,y=Axis.2, level=0.95))+
  scale_colour_manual(values=cbPalette)+
  theme_bw()+
  theme(legend.direction = 'vertical', 
        legend.key = element_rect(size=2),
        legend.key.size = unit(3, 'lines'),
        panel.grid.major = element_blank(), 
        legend.title=element_text(size=40,colour='black'),
        panel.grid.minor = element_blank(),
        legend.text=element_text(size=35),
        axis.title.y= element_text(size=40, colour='black'),
        axis.text.y = element_text(size=40, colour='black'),
        axis.ticks = element_line(colour = "black", size=2),
        axis.ticks.length = unit(0.3, "cm"),
        axis.title.x=element_text(size=40, colour='black'),
        axis.text.x = element_text(size=40, colour='black'),
        panel.border = element_rect(colour = "black", fill=NA, size=2),
        plot.title = element_text( size=40, face="bold.italic"),
        plot.margin=unit(c(1,1,1,1), "cm"))+
  ggtitle("15T FTICR_nonPolar_Treeline_Site difference")
ggsave('PCA_Treeline_Sites NonPolar.png', plot=PCA1, width= 20, height= 12)
```